A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-04-24 paper/main.tex
revision after discussion of previous state of the paper

\section*{Introduction}
\todo[inline]{Bitte am Ende (?) der Einleitung etwas zu "reproducible research" \& "datalad dataset" bringen}
Cognitive neuroimaging research is moving towards studying brain behavior
under conditions of real-life-like complexity. Motion pictures \citep{hasson2008neurocinematics} and continuous narratives \citep{honey2012not, lerner2011topographic} are increasingly utilized as so called ``naturalistic stimuli''.

@@

\todo[inline]{In der Tabelle ausführlicher beschrieben als hier (ist okay so, denke ich): ``sentences'' sind hier nicht vollständige Sätze im linguistischen Sinne (Subjekt, Prädikat), sondern auch Ausrufe ("Forrest!") oder mitunter isolierte non-speech "Sätze" ("oouh")}
For this publication, we annotated the onsets and offsets, and content of sentences, single words, and phonemes spoken in the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description (i.e. the audio-only variant of the movie)\citep{ForrestGumpDVD}(cf. table \ref{tab:overview} for an overview of the annotation's content).
fMRI data of participants watching the audio-visual movie \citep{hanke2016simultaneous} and listening to the audio-description \citep{hanke2014audiomovie} are the core data of the publicly available \textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
Additional fMRI data of this dataset include the perception of musical genres \citep{hanke2015musical}, and retinotopic mappings and localization of higher visual areas of the same participants \citep{sengupta2016extension}.

\todo[inline]{was meinst du mit: this work seems to improve/replace previous work (in part), it is important to state that clearly and identify which pieces are involved}
The current annotation facilitates modelling of hemodynamic brain responses
correlating with speech-related events in the two stimuli.
It extends already available annotations of portrayed emotions \citep{labs2015portrayed}, perceived emotions \citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the movie \citep{haeusler2016annotation}.
All annotations can be used in any study focusing on other aspects of real-life cognition by serving as additional confound measures describing key properties of major building blocks of the stimulus.

@@

\subsection*{Annotation procedure}
\todo[inline]{wo kommen die "preliminaries transcriptions" etc.? Habe die von Medusa; die "most basic" Datei, die das Dataset enthält ist wie abgesprochen der Merge aus Dialog (ungetrennte Sentences), Narrator \& Non-Speech-Annotation = \texttt{annotation/speech-vocal.csv}}
Preliminary, orthographic transcriptions of dialogues (\texttt{german\_dialog.csv}), non-speech vocalizations (e.g. laughing or groaning; \texttt{non\_speech\_vocalization.json}), and the audio-description's narrator
(\texttt{german\_audio\_description.csv}) were merged (\texttt{annotation/speech-vocal.csv}) and converted to Praat's \citep{boersma2019praat} TextGrid format  (\texttt{annotation/speech-vocal.TextGrid}).

% \href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}.
The merged transcription containing a rough onset and offset for usually a couple of sentences was edited in Praat v6.0.22 for manual validation against the original audio.
The following steps were done in several passes to iteratively improve the quality of the data:
approximate temporal onsets and offsets were corrected, and intervals containing several sentences were split into intervals containing only one sentence.
When two or more persons were speaking simultaneously the less dominant voice was dropped.
Low volume background speech (especially occurring during music or continuous environmental noise) or low volume non-speech vocalizations that are difficult to recognize by the audience were dropped, too.
\todo[inline]{what is a regular audience? without neurological disorders ;-); Simpel: eine audience, die den Film nicht 45x auf voller Lautstärke über Kopfhörer mit Transkription danebenliegend gehört hat}

% Alignment preparations
% http://prosodylab.org
% https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict
We used the Montreal Forced Aligner v1.0.1 \citep{mcauliffe2017montreal} to
algorithmically identify the exact onset of offset of the sentences, and the onset and offset of each word and phoneme embedded in the transcribed sentences.
To enable the aligner to look up the phonemes embedded within each word, we chose a German pronunciation dictionary provided by Prosodylab \citep {gorman2011prosodylab} that uses the Prosodylab PhoneSet to describe the pronounciation of phonemes.
To improve the detection rate of the automatic alignment, the dictionary was manually updated with German words that occur in the stimuli but were originally missing in the dictionary.
% \href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict}
The pronunciation of English words and phonemes occurring in the otherwise German audio track was taken from an English pronunciation dictionary (following the ARPAbet PhoneSet) provided by the Montreal Language Modeling lab (\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org}).

% Alignment
\todo[inline]{Nicht erwähnt: Wenn die Korrektur der Phoneme unmöglich war, habe ich einfach die Event-Borders zwischen den Phonemen herausgenommen. Wortbeginn und Wortende stimmen dann mit einem neuen, "künstlich-großen Phoneme" überein.
Das "Groß-Phonem" enthält dann ohne Grenzen zwischen den tatsächlichen Phonemen des Wortes alle Phoneme des Wortes ("es ist kompliziert zu erklären, aber im Grunde ganz einfach). kommt jedoch so selten vor, ist im Grunde "noise" und ist in der Anno sofort als solches zu erkennen.}
The audio track was converted from FLAC to WAV via FFmpeg v4.1.4 \citep{ffmpeg} to meet the aligner's requirements.
This WAV file, the transcription of sentences, and the updated dictionary were
submitted to the aligner that first trained an acoustic model on the data and
then performed the alignment.
The resulting .TextGrid file that contains onsets and offsets of words and phonemes was corrected manually and iteratively in several passes:
In a first step, onsets and offsets on which the automatic alignment performed moderately were corrected in Praat.
Some low volume sentences that are spoken in continuously noisy settings (pursuit, battle, hurricane, rally, disco) were removed due to poor overall alignment performance.
In a second step, the complete sentences of the orthographic transcription were copied into the annotation created by the aligner.
In a third step, the a speaker's identity was added for each sentence (cf. Table \ref{tab:speakers} for the most often occurring speakers).
During every step results from previous steps were checked again for errors.

\begin{table*}[tbp]
\caption{Overview of the annotation's content for the whole stimulus and its individual segments used during fMRI scanning. The label ``sentences'' comprises complete grammatical sentences which are additionally marked in the annotation with a full stop at the end (``my feet hurt.'').
It also comprises questions (``do you want a chocolate?''), exlamations (``run away!), or non-speech vocalizations in quick succession (``ha, ha, ha''), or in isolation (e.g. ``Forrest?'', ``Forrest!'', ``ha'') at time points when speakers switch rapidly. The label ``words'' comprises each word or non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
\label{tab:overview}
\begin{tabular}{llllllllll}
\toprule
\textbf{label} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
\midrule
sentences  & \aSentencesAll & \aSentencesI & \aSentencesII & \aSentencesIII & \aSentencesIV & \aSentencesV & \aSentencesVI & \aSentencesVII & \aSentencesVIII \tabularnewline
words  & \aWordsAll & \aWordsI & \aWordsII & \aWordsIII & \aWordsIV & \aWordsV & \aWordsVI & \aWordsVII & \aWordsVIII \tabularnewline
phonemes  & \aPhonesAll & \aPhonesI & \aPhonesII & \aPhonesIII & \aPhonesIV & \aPhonesV & \aPhonesVI & \aPhonesVII & \aPhonesVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

% NLP
% Tiger Treebank Corpus:
% \href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}.
To automatically analyze linguistic features of each words in their corresponding
sentence, we employed the Python package spaCy v2.2.1
(\href{https://spacy.io}{spacy.io}) and its accompanying German language model (\texttt{de\_core\_news\_md} that was trained on the TIGER Treebank corpus \citep{brants2004tiger}.
Non-speech vocalizations were dropped from the sentences before analysis.
We performed analyses regarding part-of-speech (i.e. grammatical tagging or word-category disambiguation), syntactic dependencies, lemmatization, word embedding (i.e. multi-dimensional meaning representation of a word), and if the word is one of the most common words of the German language (i.e. if the word is part of a stop list).
Results of these analyzes were added to the annotation which is available as a (text-based) Praat TextGrid file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid} and as a text-based, tab-separated value (TSV) formatted table (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS}) \citep{gorgolewski2016bids}).
\todo[inline]{hier bringe ich bereits vor der ``Data availability'' die Pfade/Dateinamen, weil im Folgenden die TSV-Datei in der ``Data legend'' beschrieben wird}

\subsection*{Data Legend}
The annotation in TextGrid format comprises 10 tiers: person, sentence (the text of a sentence), words (the text of a word), pos, tag, dep, lemma, stop, vector and phones (pronounciation of a phoneme).
The annotation in TSV format comprises 11 columns: onset, duration, person, text (of sentence, word or phoneme), pos, tag, dep, lemma, stop, vector.
In the following description column header labels are given in parenthesis.

@@

\subsubsection*{Text (\texttt{text})}
The text of a spoken sentence or word, or the pronounciation of a phoneme.
Phonemes of German words follow the Prosodylab PhoneSet, English words follow the ARPAbet PhoneSet.

\subsubsection*{Simple part-of-speech tag (\texttt{pos})}
A simple part-of-speech tagging (grammatical tagging; word-category disambiguation) of a word.
The simple part-of-speech tagging tags follow the Universal Dependencies v2 POS tag set (\href{https://universaldependencies.org}{universaldependencies.org}).
See Table \ref{tab:pos} for a description of the labels and the respective counts of all 15 labels.
Nouns that spaCy mistook for proper nouns or vice versa were corrected via script.
% s. list at the beginning of script
% code/add_part-of-speech-tagging2textgrid.py
Additionally in cells of this column, sentences are tagged as "SENTENCE", and phonemes are tagged as "PHONEME" to facilitate sorting, and filtering in potential further processing steps.

\begin{table*}[t]
\caption{Simple part-of-speech tagging (pos) performed by the Python package spaCy (\href{https://spacy.io}{spacy.io}).
All 15 labels sorted alpapetically.
Descriptions were taken from spaCy.explain().
Non-speech vocalizations (NONSPEECH) were manually identified.
Counts for the whole stimulus (all) and for each of the eight stimulus segments refer to the audio-description.}
\label{tab:pos}
\begin{tabular}{lllllllllll}
\toprule
textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
ADJ & \aPosAdj & \aPosAdjAll & \aPosAdjI & \aPosAdjII & \aPosAdjIII & \aPosAdjIV & \aPosAdjV & \aPosAdjVI & \aPosAdjVII \tabularnewline
ADP & \aPosAdp & \aPosAdpAll & \aPosAdpI & \aPosAdpII & \aPosAdpIII & \aPosAdpIV & \aPosAdpV & \aPosAdpVI & \aPosAdpVII & \aPosAdpVIII \tabularnewline
ADV & \aPosAdv & \aPosAdvAll & \aPosAdvI & \aPosAdvII & \aPosAdvIII & \aPosAdvIV & \aPosAdvV & \aPosAdvVI & \aPosAdvVII & \aPosAdvVIII \tabularnewline
AUX & \aPosAux & \aPosAuxAll & \aPosAuxI & \aPosAuxII & \aPosAuxIII & \aPosAuxIV & \aPosAuxV & \aPosAuxVI & \aPosAuxVII & \aPosAuxVIII \tabularnewline
CONJ & \aPosConj & \aPosConjAll & \aPosConjI & \aPosConjII & \aPosConjIII & \aPosConjIV & \aPosConjV & \aPosConjVI & \aPosConjVII & \aPosConjVIII \tabularnewline
DET & \aPosDet & \aPosDetAll & \aPosDetI & \aPosDetII & \aPosDetIII & \aPosDetIV & \aPosDetV & \aPosDetVI & \aPosDetVII & \aPosDetVIII \tabularnewline
NONSPEECH & non-speech vocalization & \aPosNonspeechAll & \aPosNonspeechI & \aPosNonspeechII & \aPosNonspeechIII & \aPosNonspeechIV & \aPosNonspeechV & \aPosNonspeechVI & \aPosNonspeechVII & \aPosNonspeechVIII \tabularnewline
NOUN & \aPosNoun & \aPosNounAll & \aPosNounI & \aPosNounII & \aPosNounIII & \aPosNounIV & \aPosNounV & \aPosNounVI & \aPosNounVII & \aPosNounVIII \tabularnewline
NUM & \aPosNum & \aPosNumAll & \aPosNumI & \aPosNumII & \aPosNumIII & \aPosNumIV & \aPosNumV & \aPosNumVI & \aPosNumVII & \aPosNumVIII \tabularnewline
PART & \aPosPart & \aPosPartAll & \aPosPartI & \aPosPartII & \aPosPartIII & \aPosPartIV & \aPosPartV & \aPosPartVI & \aPosPartVII & \aPosPartVIII \tabularnewline
PRON & \aPosPron & \aPosPronAll & \aPosPronI & \aPosPronII & \aPosPronIII & \aPosPronIV & \aPosPronV & \aPosPronVI & \aPosPronVII & \aPosPronVIII \tabularnewline
PROPN & \aPosPropn & \aPosPropnAll & \aPosPropnI & \aPosPropnII & \aPosPropnIII & \aPosPropnIV & \aPosPropnV & \aPosPropnVI & \aPosPropnVII & \aPosPropnVIII \tabularnewline
SCONJ & \aPosSconj & \aPosSconjAll & \aPosSconjI & \aPosSconjII & \aPosSconjIII & \aPosSconjIV & \aPosSconjV & \aPosSconjVI & \aPosSconjVII & \aPosSconjVIII \tabularnewline
VERB & \aPosVerb & \aPosVerbAll & \aPosVerbI & \aPosVerbII & \aPosVerbIII & \aPosVerbIV & \aPosVerbV & \aPosVerbVI & \aPosVerbVII & \aPosVerbVIII \tabularnewline
X & \aPosX & \aPosXAll & \aPosXI & \aPosXII & \aPosXIII & \aPosXIV & \aPosXV & \aPosXVI & \aPosXVII & \aPosXVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

\subsubsection*{Common Word (\texttt{stop})}
This column's cell provides information if the word is part of a stop list, hence one of the most common words in the German language or not (``True'' vs. ``False'').

\subsubsection*{Word embedding (\texttt{vector})}
% \href{https://en.wikipedia.org/wiki/Word2vec}{word vector}
A 300-dimensional word vector providing a multi-dimensional meaning representation of a word.
Out-of-vocabulary words with a vector consisting of 300 dimensions of zeroes were set to ``\#'' to save space.

\subsection*{Dataset content}
% \href{https://bids.neuroimaging.io/}{bids.neuroimaging.io}
\todo[inline]{darauf gehe ich schon am Ende von “annotation procedure” vor Datalegend ein, weil ich bereits dort erwähne, dass es zwei Versionen gibt und sich die Datalegend auf die TSV file bezieht.}
The released annotation comes in two different versions. First, as a text-based TextGrid file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid}) to be conveniently edited with the software Praat \citep{boersma2019praat}.
Second, as a text-based tab-separated-value (TSV) formatted table  (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with the brain imaging data structure BIDS \citep{gorgolewski2016bids}
The source code for all descriptive statistics included in this paper is available in \texttt{code/descriptive-statistics.py} (Python script).

\section*{Dataset validation}
% Information about any validation carried out and/or any limitations of the
% datasets, including any allowances made for controlling bias or unwanted
% sources of variability.
% ~170 words => das wird beim folgenden Schreiben definitiv nichts werden
% Intro
In order to assess data quality, we investigated if contrasting speech-related events to events without speech lead to increased activation in areas known to be involved in semantic processing \citep{hickok2007cortical}.
Moreover, we tested if similar linguistic concepts providing high semantic information (proper nouns and nouns) contrasted to a concept providing low semantic information (coordinate conjunctions) lead to increased activation in congruent brain areas.
% Preprocessing
\todo[inline]{die Daten aus Hanke2014 sind nicht bewegungskorrigiert und nicht  aligned. Quelle ist in vorliegendem Falle:
juseless.inm7.de:/data/project/studyforrest/collection/phase1}
\todo[inline]{bei allem, was folgend mit alignment/co-registration zu tun hat, bin ich mir nicht sicher \& gehe ggf. zu wenig auf den Prozess der Template Erstellung und des alignments ein; vgl. Review zum Muscial Genre Paper}
\todo[inline]{hanke2014 spricht von 20 subjects (age 21–38 years, mean age 26.6 years, 12 male), es fehlt hier aber sub-10}
We used fMRI BOLD data of the 2h audio-description (\unit[7]{Tesla}, TR=\unit[2]{s}, 3599 volumes, 36 axial slices, thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane resolution, \unit[224]{mm} field-of-view) of 19 healthy subjects \citep{hanke2014audiomovie} that were already corrected for motion and aligned [+++wie?+++] to study specific group template [+++co-registered to MNI?+++].

All further analysis steps were carried out using Feat v6.00 (FMRI Expert Analysis Tool)\citep{woolrich2001autocorr} as part of FSL v5.0.9 (FMRIB's Software Library)\citep{smith2004fsl}.
Data were temporally high-pass filtered (cut-off \unit[150]{s}), spatially smoothed (Gaussian kernel; \unit[4.0]{mm} FWHM), and the brain was extracted from surrounding tissue [+++kein Plan, ob die Reihenfolge so korrekt ist].
A grand-mean intensity normalization of the entire 4D dataset was performed by a single multiplicative factor.

>>>>

\section*{Introduction}
Cognitive neuroimaging research is moving towards studying brain behavior
under conditions of real-life-like complexity. Motion pictures \citep{hasson2008neurocinematics} and continuous narratives \citep{honey2012not, lerner2011topographic} are increasingly utilized as so called ``naturalistic stimuli''.

@@

\todo[inline]{Ausführliche Beschreibung bzgl. Sentences in Tabelle; ich finde es in der Form hier so ok/besser.}
For this publication, we annotated the exact onsets and offsets, and content of sentences, single words, and phonemes spoken in the audio-visual movie ``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description (i.e. the audio-only variant of the movie)\citep{ForrestGumpDVD}(see Table \ref{tab:overview} for an overview of the annotation's content).
fMRI data of participants watching the audio-visual movie \citep{hanke2016simultaneous} and listening to the audio-description \citep{hanke2014audiomovie} are the core data of the publicly available \textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
Additional fMRI data of this dataset include the perception of musical genres \citep{hanke2015musical}, and retinotopic mappings and localization of higher visual areas of the same participants \citep{sengupta2016extension}.

\todo[inline]{this work seems to improve/replace previous work (in part), it is important to state that clearly and identify which pieces are involved => es ist implizit im Text, der von “exact onset \& offsets” und weiter unten von “preliminary annotations” gesprochen wird; keine Ahnung, ob man kommunizieren sollte, dass die preliminary Dinger mal auf github waren; war jedenfalls nicht offensichtlich, beworben o.ä.}
The current annotation facilitates modelling of hemodynamic brain responses
correlating with speech-related events in the two stimuli.
It extends already available annotations of portrayed emotions \citep{labs2015portrayed}, perceived emotions \citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the movie \citep{haeusler2016annotation}.
All annotations can be used in any study focusing on other aspects of real-life cognition by serving as additional confound measures describing key properties of major building blocks of the stimulus.

@@

\subsection*{Annotation procedure}
Preliminary, manual orthographic transcriptions of dialogues, non-speech vocalizations (e.g. laughing or groaning) and script for the audio-description's narrator were merged, and converted to Praat's \citep{boersma2019praat} TextGrid format.

% \href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}.
The merged transcription containing a rough onset and offset for usually a couple of sentences was edited in Praat for manual validation against the original audio.
The following steps were done in several passes to iteratively improve the quality of the data:
approximate temporal onsets and offsets were corrected, and intervals containing several sentences were split into intervals containing only one sentence.
When two or more persons were speaking simultaneously the less dominant voice was dropped.
Low volume background speech (especially occurring during music or continuous environmental noise) or low volume non-speech vocalizations which were subjectively assessed to be incomprehensible for the audience were dropped, too.

% Alignment preparations
% http://prosodylab.org
% https://raw.githubusercontent.com/prosodylab/prosodylab.dictionaries/master/de.dict
We used the Montreal Forced Aligner \citep{mcauliffe2017montreal} to
algorithmically identify the exact onset of offset of the sentences, and the onset and offset of each word and phoneme embedded in the transcribed sentences.
To enable the aligner to look up the phonemes embedded within each word, we chose a German pronunciation dictionary provided by Prosodylab \citep {gorman2011prosodylab} that uses the Prosodylab PhoneSet to describe the pronounciation of phonemes.
To improve the detection rate of the automatic alignment, the dictionary was manually updated with German words that occur in the stimuli but were originally missing in the dictionary.
% \href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org/mfa/dictionaries/english.dict}
The pronunciation of English words and phonemes occurring in the otherwise German audio track was taken from an English pronunciation dictionary (following the ARPAbet PhoneSet) provided by the Montreal Language Modeling lab (\href{http://mlmlab.org/mfa/dictionaries/english.dict}{mlmlab.org}).

% Alignment
The audio track was converted from FLAC to WAV via FFmpeg \citep{ffmpeg} to meet the aligner's requirements.
This WAV file, the transcription of sentences, and the updated dictionary were
submitted to the aligner that first trained an acoustic model on the data and
then performed the alignment.
The resulting .TextGrid file that contains onsets and offsets of words and phonemes was corrected manually and iteratively in several passes:
In a first step, onsets and offsets on which the automatic alignment performed moderately were corrected in Praat.
Some low volume sentences that are spoken in continuously noisy settings (pursuit, battle, hurricane, rally, disco) were removed due to poor overall alignment performance.
In a second step, the complete sentences of the orthographic transcription were copied into the annotation created by the aligner.
In a third step, the a speaker's identity was added for each sentence (see Table \ref{tab:speakers} for the most often occurring speakers).
During every step results from previous steps were checked again for errors.

\begin{table*}[tbp]
    \caption{Overview of the annotation's content for the whole stimulus and its individual segments used during fMRI scanning. The category \texttt{sentences} comprises complete grammatical sentences which are additionally marked in the annotation with a full stop at the end (``my feet hurt.'').
    It also comprises questions (``do you want a chocolate?''), exlamations (``run away!), or non-speech vocalizations in quick succession (``ha, ha, ha''), or in isolation (e.g. ``Forrest?'', ``Forrest!'', ``ha'') at time points when speakers switch rapidly. The category \texttt{words} comprises each word or non-speech vocalization (N=\aPosNonspeechAll) in isolation.}
\label{tab:overview}
\begin{tabular}{llllllllll}
\toprule
\textbf{category} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8}\\
\midrule
sentences  & \aSentencesAll & \aSentencesI & \aSentencesII & \aSentencesIII & \aSentencesIV & \aSentencesV & \aSentencesVI & \aSentencesVII & \aSentencesVIII \tabularnewline
words  & \aWordsAll & \aWordsI & \aWordsII & \aWordsIII & \aWordsIV & \aWordsV & \aWordsVI & \aWordsVII & \aWordsVIII \tabularnewline
phonemes  & \aPhonesAll & \aPhonesI & \aPhonesII & \aPhonesIII & \aPhonesIV & \aPhonesV & \aPhonesVI & \aPhonesVII & \aPhonesVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

% NLP
% Tiger Treebank Corpus:
% \href{https://www.ims.uni-stuttgart.de}{ims.uni-stuttgart.de}.
To automatically analyze linguistic features of each words in their corresponding
sentence, we employed the Python package spaCy \citep{spacy2} and its accompanying German language model (\texttt{de\_core\_news\_md} that was trained on the TIGER Treebank corpus \citep{brants2004tiger}.
Non-speech vocalizations were dropped from the sentences before analysis.
We performed analyses regarding part-of-speech (i.e. grammatical tagging or word-category disambiguation), syntactic dependencies, lemmatization, word embedding (i.e. multi-dimensional meaning representation of a word), and if the word is one of the most common words of the German language (i.e. if the word is part of a stop list).

\subsection*{Data Legend}
\todo[inline]{Minimale Info hier, dass es zwei Versionen gibt und sich der folgende Abschnitt auf TSV file bezieht}
The annotation is available in two different versions, both providing the same information: a) as a (text-based) Praat TextGrid file and b) as a text-based, tab-separated value (TSV) formatted table.
The following descriptions refer to the ten columns of the TSV file, namely
\texttt{onset}, \texttt{duration}, \texttt{person}, \texttt{text} (of sentence, word or phoneme), \texttt{pos}, \texttt{tag}, \texttt{dep}, \texttt{lemma}, \texttt{stop}, \texttt{vector}.

@@

\subsubsection*{Text (\texttt{text})}
\todo[inline]{Großphoneme erwähnen;Nicht erwähnt: Wenn die Korrektur der Phoneme unmöglich war, habe ich einfach die Event-Borders zwischen den Phonemen herausgenommen. Wortbeginn und Wortende stimmen dann mit einem neuen, "künstlich-großen Phoneme" überein.
Das "Groß-Phonem" enthält dann ohne Grenzen zwischen den tatsächlichen Phonemen des Wortes alle Phoneme des Wortes ("es ist kompliziert zu erklären, aber im Grunde ganz einfach). kommt jedoch so selten vor, ist im Grunde "noise" und ist in der Anno sofort als solches zu erkennen.}
The text of a spoken sentence or word, or the pronounciation of a phoneme.
Phonemes of German words follow the Prosodylab PhoneSet, English words follow the ARPAbet PhoneSet.

\subsubsection*{Simple part-of-speech tag (\texttt{pos})}
A simple part-of-speech tagging (grammatical tagging; word-category disambiguation) of a word.
The simple part-of-speech tagging tags follow the Universal Dependencies v2 POS tag set (\href{https://universaldependencies.org}{universaldependencies.org}).
See Table \ref{tab:pos} for a description of the labels and the respective counts of all 15 labels.
Nouns that spaCy mistook for proper nouns or vice versa were corrected via script.
% s. list at the beginning of script
% code/add_part-of-speech-tagging2textgrid.py
Additionally in cells of this column, sentences are tagged as \texttt{SENTENCE}, and phonemes are tagged as \texttt{PHONEME} to facilitate sorting, and filtering in potential further processing steps.

\begin{table*}[t]
\caption{Simple part-of-speech tagging (\texttt{pos}) performed by the Python package spaCy \citep{spacy2}.
All 15 labels sorted alpapetically.
Descriptions were taken from spaCy.explain().
Non-speech vocalizations (\texttt{NONSPEECH}) were manually identified.
Counts for the whole stimulus (\texttt{all}) and for each of the eight stimulus segments refer to the audio-description.}
\label{tab:pos}
\begin{tabular}{lllllllllll}
\toprule
\textbf{label} & \textbf{description} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
ADJ & \aPosAdj & \aPosAdjAll & \aPosAdjI & \aPosAdjII & \aPosAdjIII & \aPosAdjIV & \aPosAdjV & \aPosAdjVI & \aPosAdjVII \tabularnewline
ADP & \aPosAdp & \aPosAdpAll & \aPosAdpI & \aPosAdpII & \aPosAdpIII & \aPosAdpIV & \aPosAdpV & \aPosAdpVI & \aPosAdpVII & \aPosAdpVIII \tabularnewline
ADV & \aPosAdv & \aPosAdvAll & \aPosAdvI & \aPosAdvII & \aPosAdvIII & \aPosAdvIV & \aPosAdvV & \aPosAdvVI & \aPosAdvVII & \aPosAdvVIII \tabularnewline
AUX & \aPosAux & \aPosAuxAll & \aPosAuxI & \aPosAuxII & \aPosAuxIII & \aPosAuxIV & \aPosAuxV & \aPosAuxVI & \aPosAuxVII & \aPosAuxVIII \tabularnewline
CONJ & \aPosConj & \aPosConjAll & \aPosConjI & \aPosConjII & \aPosConjIII & \aPosConjIV & \aPosConjV & \aPosConjVI & \aPosConjVII & \aPosConjVIII \tabularnewline
DET & \aPosDet & \aPosDetAll & \aPosDetI & \aPosDetII & \aPosDetIII & \aPosDetIV & \aPosDetV & \aPosDetVI & \aPosDetVII & \aPosDetVIII \tabularnewline
NONSPEECH & non-speech vocalization & \aPosNonspeechAll & \aPosNonspeechI & \aPosNonspeechII & \aPosNonspeechIII & \aPosNonspeechIV & \aPosNonspeechV & \aPosNonspeechVI & \aPosNonspeechVII & \aPosNonspeechVIII \tabularnewline
NOUN & \aPosNoun & \aPosNounAll & \aPosNounI & \aPosNounII & \aPosNounIII & \aPosNounIV & \aPosNounV & \aPosNounVI & \aPosNounVII & \aPosNounVIII \tabularnewline
NUM & \aPosNum & \aPosNumAll & \aPosNumI & \aPosNumII & \aPosNumIII & \aPosNumIV & \aPosNumV & \aPosNumVI & \aPosNumVII & \aPosNumVIII \tabularnewline
PART & \aPosPart & \aPosPartAll & \aPosPartI & \aPosPartII & \aPosPartIII & \aPosPartIV & \aPosPartV & \aPosPartVI & \aPosPartVII & \aPosPartVIII \tabularnewline
PRON & \aPosPron & \aPosPronAll & \aPosPronI & \aPosPronII & \aPosPronIII & \aPosPronIV & \aPosPronV & \aPosPronVI & \aPosPronVII & \aPosPronVIII \tabularnewline
PROPN & \aPosPropn & \aPosPropnAll & \aPosPropnI & \aPosPropnII & \aPosPropnIII & \aPosPropnIV & \aPosPropnV & \aPosPropnVI & \aPosPropnVII & \aPosPropnVIII \tabularnewline
SCONJ & \aPosSconj & \aPosSconjAll & \aPosSconjI & \aPosSconjII & \aPosSconjIII & \aPosSconjIV & \aPosSconjV & \aPosSconjVI & \aPosSconjVII & \aPosSconjVIII \tabularnewline
VERB & \aPosVerb & \aPosVerbAll & \aPosVerbI & \aPosVerbII & \aPosVerbIII & \aPosVerbIV & \aPosVerbV & \aPosVerbVI & \aPosVerbVII & \aPosVerbVIII \tabularnewline
X & \aPosX & \aPosXAll & \aPosXI & \aPosXII & \aPosXIII & \aPosXIV & \aPosXV & \aPosXVI & \aPosXVII & \aPosXVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

\subsubsection*{Common Word (\texttt{stop})}
This column's cell provides information if the word is part of a stop list, hence one of the most common words in the German language or not (\texttt{True} vs. \texttt{False}).

\subsubsection*{Word embedding (\texttt{vector})}
% \href{https://en.wikipedia.org/wiki/Word2vec}{word vector}
A 300-dimensional word vector providing a multi-dimensional meaning representation of a word.
Out-of-vocabulary words with a vector consisting of 300 dimensions of zeroes were set to \texttt{\#} to save space.

\subsection*{Dataset content}
% \href{https://bids.neuroimaging.io/}{bids.neuroimaging.io}
The released annotation comes in two different versions. First, as a text-based TextGrid file (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.TextGrid}) to be conveniently edited with the software Praat \citep{boersma2019praat}.
Second, as a text-based, tab-separated-value (TSV) formatted table  (\texttt{annotation/fg\_rscut\_ad\_ger\_speech\_tagged.tsv}) in accordance with the brain imaging data structure (\href{https://bids.neuroimaging.io/}{BIDS} \citep{gorgolewski2016bids}).
The source code for all descriptive statistics included in this paper is available in \texttt{code/descriptive-statistics.py} (Python script).

\section*{Dataset validation}
% Information about any validation carried out and/or any limitations of the
% datasets, including any allowances made for controlling bias or unwanted
% sources of variability.
% ~170 words => das wird beim folgenden Schreiben definitiv nichts werden
% Intro
In order to assess data quality, we investigated if contrasting speech-related events to events without speech lead to increased activation in areas known to be involved in semantic processing \citep{hickok2007cortical}.
Moreover, we tested if similar linguistic concepts providing high semantic information (proper nouns and nouns) contrasted to a concept providing low semantic information (coordinate conjunctions) lead to increased activation in congruent brain areas.
% Preprocessing
\todo[inline]{hanke2014 spricht von 20 subjects (age 21–38 years, mean age 26.6 years, 12 male), es fehlt hier aber sub-10}
% Details of the alignment procedure are given in the section on “Technical Validation”.
%Data aligned by applying an affine transformation only are available in bold_dico_dico7Tad2grpbold7Tad.nii.gz.
% Data aligned by non-linear warping are available in bold_dico_dico7Tad2grpbold7Tad_nl.nii.gz.
We used blood oxygenation level-dependent (BOLD) functional magnetic resonance imaging (fMRI) data of the 2h audio-description (\unit[7]{Tesla}, \unit[2]{s} repetition time, 3599 volumes, 36 axial slices, thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane resolution, \unit[224]{mm} field-of-view) of 19 healthy subjects \citep{hanke2014audiomovie}.
Data were already corrected for motion at the scanner computer.
Further, individual BOLD time-series were already aligned by non-linear warping to a study-specific T2*-weighted echo planar imaging (EPI) group template (cf. \citep{hanke2014audiomovie} for details on how the group template was created).
\todo[inline]{So korrekt und “vollständig? MNI152 co-registration? Im Übrigen finde ich 3-4 Paper, die als Zitation für den MNI152-space in Frage kommen, wobei keines richtig passen will; hanke2014 zitiert keines}
All further analysis steps were carried out using Feat v6.00 (FMRI Expert Analysis Tool)\citep{woolrich2001autocorr} as part of FSL v5.0.9 (FMRIB's Software Library)\citep{smith2004fsl}.
Data were temporally high-pass filtered (cut-off \unit[150]{s}), spatially smoothed (Gaussian kernel; \unit[4.0]{mm} FWHM), and the brain was extracted from surrounding tissue [+++kein Plan, ob die Reihenfolge so korrekt ist].
A grand-mean intensity normalization of the entire 4D dataset was performed by a single multiplicative factor.
